Synthesizing Symmetric Lenses

### 2019-02-28 papers/SymmetricLenses/main.tex
react to feedback and make safer statements

Formally, we characterize the expressiveness of simple symmetric lenses by
proving that they are exactly the symmetric lenses
that satisfy an intuitive property called \emph{forgetfulness}.  We also show
they are expressive enough for many practical uses by adding simple
symmetric lenses to 
the Boomerang language~\cite{boomerang} and applying them to a range of
real-world applications.  This exercise also demonstrates that simple
symmetric lenses integrate smoothly with other advanced lens features
provided by Boomerang, including {\em quotient
  lenses}~\cite{quotientlenses,maina+:quotient-synthesis} and {\em matching
  lenses}~\cite{matchinglenses}.\bcp{How does it demonstrate this?  Did we
  actually {\em use} symmetric quotient or matching lenses for anything?  Or
are we just observing that these features can coexist in the same
implementation even if using them together might not make sense?}

@@

For these, we turn to information theory. We consider ``likely'' lenses to
be ones that propagate ``a lot'' of information 
from the left data format to the right and vice versa. Conversely, ``unlikely''
lenses are ones that require a large amount of additional information to recover
one of the formats given the other. \bcp{Next two sentences are not very
  persuasive.  And they may be a bit out of date anyway, not that we have
  these annotations.  We can just say that we take ``propagate as much as
  possible'' as the default and use explicit annotations on the source and
  target types to mark information that the user knows should not be propagated.}For many application scenarios, users
will want to synchronise formats with lots of shared information (and lenses
with little shared information are typically easier to write). Our tool is built
primarily for these complex scenarios, and so lenses that propagate more
information are preferable in our context to ones that propagate less.
%
This intuition is formalized using \emph{stochastic regular expressions}
(SREs)~\cite{stoch-rnn,stoch-def}, which simultaneously define a set of
strings and a probability distribution over those strings.  Using this
probability distribution, we can calculate the likelihood of a given lens.

>>>>

Formally, we characterize the expressiveness of simple symmetric lenses by
proving that they are exactly the symmetric lenses
that satisfy an intuitive property called \emph{forgetfulness}.  We also show
they are expressive enough for many practical uses by adding simple
symmetric lenses to 
the Boomerang language~\cite{boomerang} and applying them to a range of
real-world applications.  This exercise also demonstrates that simple
symmetric lenses can coexist with, and be extended by, other advanced lens features
provided by Boomerang, including {\em quotient
  lenses}~\cite{quotientlenses,maina+:quotient-synthesis} and {\em matching
  lenses}~\cite{matchinglenses}.\bcp{How does it demonstrate this?  Did we
  actually {\em use} symmetric quotient or matching lenses for anything?  Or
are we just observing that these features can coexist in the same
implementation even if using them together might not make sense?}
\afm{Good point, updated.}

@@

For these, we turn to information theory. We consider ``likely'' lenses to
be ones that propagate ``a lot'' of information 
from the left data format to the right and vice versa. Conversely, ``unlikely''
lenses are ones that require a large amount of additional information to recover
one of the formats given the other. By default, our synthesis algorithm prefers
the lenses that propagate more information.
This preference is formalized using \emph{stochastic regular expressions}
(SREs)~\cite{stoch-rnn,stoch-def}, which simultaneously define a set of
strings and a probability distribution over those strings.  Using this
probability distribution, we can calculate the likelihood of a given lens.
